Periodograms for Multiband Astronomical Time Series

### 2015-05-15 writeup/paper.tex
add references to figure 9 caption

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig09.pdf}
  \caption{
    Fraction of periods correctly determined for LSST RR Lyrae as a function
    of the length of the observing season and the mean $g$-band magnitude, for the multiband (solid lines)
    and single-band supersmoother (dashed lines) approaches.
    The multiband method is superior to the single-band supersmoother approach in all cases, and especially for the faintest objects.
  } 
  \figlabel{LSST_sims}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig09.pdf}
  \caption{
    Fraction of periods correctly determined for LSST RR Lyrae as a function
    of the length of the observing season and the mean $g$-band magnitude, for the multiband periodogram approach \new{(method of this work; solid lines)}
    and single-band supersmoother approach \new{\citep[method of][dashed lines]{Oluseyi12}}.
    The multiband method is superior to the single-band supersmoother approach in all cases, and especially for the faintest objects.
  } 
  \figlabel{LSST_sims}
\end{figure}
